Deriving Random Generators via\\ Higher-Level Representations

### 2019-01-22 paper/introduction.tex
WIP - Intro

Aliquam erat volutpat. Nunc eleifend leo vitae magna. In id erat non orci
commodo lobortis. Proin neque massa, cursus ut, gravida ut, lobortis eget,
lacus. Sed diam. Praesent fermentum tempor tellus. Nullam tempus. Mauris ac
felis vel velit tristique imperdiet. Donec at pede. Etiam vel neque nec dui
dignissim bibendum. Vivamus id enim. Phasellus neque orci, porta a, aliquet
quis, semper a, massa. Phasellus purus. Pellentesque tristique imperdiet tortor.
Nam euismod tellus id erat\cite{grieco2017}.

@@

>>>>

% Scenario of random testing
Random testing is a promising approach to finding bugs {\tocite}.
%
QuickCheck \cite{ClaessenH00} is a dominant tool of this sort used by the
Haskell community.
%
It requires developers to specify testing properties which describe programs
behavior and random data generator based on the \emph{type} of the expected
inputs. %, e.g., an integer, an string, or an abstract data type (ADT).
%
QuickCheck then generates a large number of random \emph{test cases} and reports
those violating testing properties.
%

% Situation with Quick Check, ADTs, tools
While QuickCheck comes equipped with random generators for built-in types, there
exists additional tools to automatically derive generators for user-defined
abstract data types (ADT) (e.g.,
\cite{mitchell2007,RuncimanNL08,DuregardJW12,grieco2017,DBLP:conf/haskell/MistaRH18}).
%
The main difference about these tools lies on the guarantees provided when it
comes to ensuring a terminating generation process or distribution of the random
values.
%
When generating ADT values, these tools guarantee that such values are
\emph{well-typed}.
%
In that manner, generated values follow the structure described by the
definition of the ADT, which proves useful when testing software with highly
structured inputs like compilers \cite{Palka11,MidtgaardJKNN17}.
%
Generating values from ADTs also proves to be a fruitful approach when looking
for vulnerabilities with fuzzers \cite{GriecoCB16,grieco2017}.
%

%% Problem

%% Our proposal

@@

% Local Variables:
% TeX-master: "main.lhs.tex"
% TeX-command-default: "Make"
% End:
